### 2016-03-10 manuscript.Rnw
move citation at end of the sentence for clarity

The Open Tree of Life (OTL) project aims at assembling and synthesizing our
current understanding of phylogenetic relationships across all organisms on
Earth \citep{Hinchliff2015}, while providing tools and services that facilitate
access to this information. OTL combines taxonomic information that serves as
the backbone for the phylogenetic relationships, and published phylogenies to
elucidate relationships among taxa. This combination of information is used to
structure the comprehensive synthetic tree. Studies can be contributed to the
synthetic tree through a curator interface
(\url{https://tree.opentreeoflife.org/curator}), allowing the synthetic tree to
be continuously updated as relationships are elucidated or reevaluated. The
current draft of the OTL synthetic tree contains 2.3 million tips. Beyond
obvious applications across the life sciences to explore questions in evolution,
biodiversity, and conservation, the resources OTL provides are useful for
education and outreach (e.g., illustrating course material, or developing
outreach activities to explore relationships among species).

>>>>

The Open Tree of Life (OTL) project aims at assembling and synthesizing our
current understanding of phylogenetic relationships across all organisms on
Earth while providing tools and services that facilitate access to this
information \citep{Hinchliff2015}. OTL combines taxonomic information that
serves as the backbone for the phylogenetic relationships, and published
phylogenies to elucidate relationships among taxa. This combination of
information is used to structure the comprehensive synthetic tree. Studies can
be contributed to the synthetic tree through a curator interface
(\url{https://tree.opentreeoflife.org/curator}), allowing the synthetic tree to
be continuously updated as relationships are elucidated or reevaluated. The
current draft of the OTL synthetic tree contains 2.3 million tips. Beyond
obvious applications across the life sciences to explore questions in evolution,
biodiversity, and conservation, the resources OTL provides are useful for
education and outreach (e.g., illustrating course material, or developing
outreach activities to explore relationships among species).
